### 2013-06-12 ms_V3.tex

This feature is particularly important to understand global change impacts on community structure. For instance, a common prediction of the impact of fisheries on the body size distribution is the reduction in the average and variance of body size \parencite{Jackson2001}. Similarly, global warming is also expected to alter fish body size distribution towards smaller species \parencite{Cheung2012}. We explored by simulations the impact of these changes on the degree distribution of the Mediterranean metaweb. Results are illustrated at Fig. 6. The shape of the cumulative degree distribution provides a visual assessment of the distribution of diet specificity in a network. The curves becomes steeper and the fall moves to the left with increasing specialization (indicative of a larger proportion of species with a low degree). Even if the simulated scenarios are crude representations of the predicted alterations of community structure, they both show that fisheries impacts on body size will substantially alter the network properties. The results at Fig. 6 show that reduction in the average body size will decrease the average number of preys per predator (there is an initial sharper decline of the cumulative distribution), but that super generalist species will also appear (because of the shift of the tail toward the right). The removal of the 40\% largest species reduces much more the average generality which is expect as larger species are predators with a large feeding niche in the niche model. The two scenarios consequently increases substantially the relative abundance of species with a smaller degree, even for the average size reduction scenario where the total number of species is held constant. The change in the degree distribution is likely to reduce substantially the expected persistence and stability of these communities \parencite{Gravel2011a, Gravel2011b}.

@@

\subsection*{Figure 2}
Example of predator-prey body size relationship and predictions from the parameterized niche model. Black dots represent observed links while open dots are predicted interactions based on the parameterization of the niche model. The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not pbservation ("b") and an open circle a non-predicted and observed link ("c"). Data from a creek bed located in Australia \parencite{Brose2005}.

>>>>

This feature is particularly important to understand global change impacts on community structure. For instance, a common prediction of the impact of fisheries on the body size distribution is the reduction in the average and variance of body size \parencite{Jackson2001}. Similarly, global warming is also expected to alter fish body size distribution towards smaller species \parencite{Cheung2012}. We explored by simulations the impact of these changes on the degree distribution of the Mediterranean metaweb. Results are illustrated at Fig. 6. The shape of the cumulative degree distribution provides a visual assessment of the distribution of diet specificity in a network. The curves becomes steeper and the fall moves to the left with increasing specialization (indicative of a larger proportion of species with a low degree). Even if the simulated scenarios are crude representations of the predicted alterations of community structure, they both show that fisheries impacts on body size will substantially alter the network properties. The results at Fig. 6 show that reduction in the average body size will decrease the average number of preys per predator (there is an initial sharper decline of the cumulative distribution), but that super generalist species will also appear (because of the shift of the tail toward the right). The removal of the 40\% largest species reduces much more the average generality which is expected as larger species are predators with a large feeding niche in the niche model. The two scenarios consequently increases substantially the relative abundance of species with a smaller degree, even for the average size reduction scenario where the total number of species is held constant. The change in the degree distribution is likely to reduce substantially the expected persistence and stability of these communities \parencite{Gravel2011a, Gravel2011b}.

@@

\subsection*{Figure 2}
Example of predator-prey body size relationship and predictions from the parameterized niche model. Black dots represent observed links while open dots are predicted interactions based on the parameterization of the niche model. The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not observation ("b") and an open circle a non-predicted and observed link ("c"). Data from a creek bed located in Australia \parencite{Brose2005}.
